discussion

### 2018-04-17 man/ms_3_discussion.Rmd
update
update discussion and bib file

#### Climate and tree relationship 
Frase de resultados que tenemos que poner en discussion: 
Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth (Figure 7b), specially for the northern population (r > 0.6), ... **which can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014]**.

>>>>

#### Climate and tree relationship

Frase de resultados que tenemos que poner en discussion: 
Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth (Figure 7b), specially for the northern population (r > 0.6), ... **which can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014]**.

Moisture availability has been reported as the most limiting factor driving radial growth of *Q. pyrenaica* along their distribution range in Iberian Peninsula [@GeaIzquierdo2014]. We found a singnificant positive relation between precipitacion (hydrological year and previous December) and tree-growth (Figure 6a). Our results are consistent with previous studies highlighting the influence of precipitation on tree-ring growth [@Roig2009; @GeaIzquierdo2014; @GeaIzquierdo2014FEM; @Leal2015; @Camison2016; @GonzalezGonzalez2014; @GarciaGonzalez2017]
